Probabilistic Model of Bilateral Lymphatic Spread in Head and Neck Cancer

### 2024-12-09 manuscript.qmd
add draft of thanks to appendix

This work was supported by:

>>>>

We want to thank the research group around Vincent Grégoire from the Centre Léon Bérard in Lyon (France) and Roland Giger's group from the Inselspital in Bern (Switzerland) for collecting, curating, and publishing their data on lymphatic progression patterns. Without their pathologically assessed data on nodal involvement, we could not have trained and validated our model with a large and representative cohort.

Further, this work was supported by:
